Title here

### 2016-12-06 portfolio/text/ms.Rmd
More writing

@@

### Something about overall model fit

- Parameters from hierarchical model (main: Fig. S\ref{fig:fe}, varying: S\ref{fig:re})
- Residuals clearly show pattern that we see in the parameter estimates (Fig. S\ref{fig:resid})
- Downside residuals look very similar and justify using the full data set
(upside and downside) (Fig. S\ref{fig:resid-downside})
- Mention the year-permit varying intercepts and what they mean
(Fig. S\ref{fig:str-yrs}) --- good and bad years where
everyone in that strategy tended to do better or worse ---
this accounts for that and therefore compares everything to
the expected revenue for that year

@@

**Fig. \ref{fig:within} - within strategies**

- fish more days, make more money (Fig. S\ref{fig:fe})
- after accounting for days fished, most commonly,
specializing is associated with higher revenue,
but sometimes the reverse (Fig. \ref{fig:within})
- if we don't account for changes in effort, then higher species diversity
means more money fairly consistently (TODO make figure)
- changing species diversity (number of species fished or evenness of species
fished) tends to be associated with greater variability / uncertainty
year-to-year (Figs. \ref{fig:within}, S\ref{fig:fe})
- increasing species diversity within
the constraints of a permit set has a fishery-dependent effect on revenue and
is usually (`r g2_dens`% probability)
associated with increased uncertainty in revenue.
(Fig. \ref{fig:within})

>>>>

*TODO: for the following into the results section or and the method section with
this:*

Residuals from the mean component of our model clearly show the "V"-shaped
pattern that the variance component of our model seeks to capture (Fig.
S\ref{fig:resid}). Furthermore, the downside residuals (year-individual data
points with lower than expected revenue) look qualitatively similar to the
complete set of residuals (upside and downside) (Fig.
S\ref{fig:resid-downside}). Therefore, it seemed appropriate to model the
variability as a proxy for revenue risk.

The estimated year-permit intercepts represent years when people
with a particular permit set in a given year tended to do better or worse than
the long-term average for that permit set (Fig. S\ref{fig:str-yrs}). Therefore,
an individual's expected revenue and variability is after accounting for the
general trend in revenue for that permit set.

Our model estimates overall average effects (Fig. S\ref{fig:fe}) and effects
that vary by permit set (Fig. S\ref{fig:re}).

@@

@@

In contrast to the clear effect of species diversity on revenue variability when
comparing across fishing strategies, the effect of changing fished species
diversity for an individual *within* the constraints of a given permit set is
more variable (Fig. \ref{fig:within}). After accounting for fishing effort (Fig.
S\ref{fig:fe}), specializing (decreasing species diversity) tends to be
associated with increased revenue (`r g2_dens`% probability; Fig.
\ref{fig:within}). This was particularly clear for permits where individuals
tend to specialize on sockeye salmon: individuals with setnet permits for salmon
in Prince William Sound, Cook Inlet, Kodiak, Bristol Bay, or the Alaska
Peninsula experienced a ~1.5% increase in revenue for a 1% decrease in fished
species diversity (Fig. \ref{fig:within}B). The converse was usually true ---
generalizing tends to be associated with lower expected revenue after accounting
for fishing effort (i.e. Fig. \ref{fig:within}A and \ref{fig:within}B are nearly
mirror images left to right). This specializing benefit on revenue is only
apparent after accounting for fishing effort. Given that fishing for more
species tends to be associated with increased fishing effort, generalizing tends
to be associated with higher revenue when not standardizing for fishing effort
(Fig. S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) one's
fished species diversity within the constraints of a permit set tends to be
associated with greater expected variability or uncertainty in year-to-year
revenue (Fig. \ref{fig:within} strategies above 0, Fig. S\ref{fig:fe}). This
effect was strongest for individuals with a halibut longline permit or halibut
and sablefish longline permits. Individuals with these strategies experienced
~2% increase in standardized variability for a 1% change in fished species
diversity. Fished species diversity for these permits is primarily in the form
of bycatch.

The Alaskan halibut and sablefish fisheries were rationalized in 199X --- they
switched from XX to a individual fishery quota (IFQ) system. We refit our models
allowing all effects to vary separately before and after 19XX for strategies
involving these permits (i.e. treating them as separate strategies). Variability
was reduced by ~25% (XX--XX 95% CI) after the introduction of these IFQs
compared to before for individuals with only a halibut or sablefish permit (Fig.
SX). The cost of changing fished species diversity for an individual in terms of
the effect on revenue variability increased after the introduction of IFQs for
all strategies, and especially for individuals fishing only halibut and
sablefish (Fig. SX).
